Report

### 2014-11-08 MSLLReport.tex
Add sth about maximum entropy

	\begin{frame}[shrink]
		\frametitle{What is entropy(6)}
		Let's consider
		\begin{eqnarray*}
			&& H(Y)-I(X,Y)  \\
			&=& -\sum_y p(y)\log p(y) - \sum_{x,y}\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_y\left(\sum_x p(x,y)\right)\log p(y) - \sum_{x,y}p(x,y)\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_{x,y}p(x,y)\log p(y) - \sum_{x,y}\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_{x,y}p(x,y)\log\frac{p(x,y)}{p(x)} \\
			&=& -\sum_{x,y}p(x,y)\log p(y|x) = H(Y|X)
		\end{eqnarray*}
		According the formula (7):
		$$I(X,Y) = H(X)+H(Y)-H(X,Y)$$
	\end{frame}
\end{document}

>>>>

	\begin{frame}[shrink]
		\frametitle{What is entropy(6)}
		Let's consider
		\begin{eqnarray*}
			&& H(Y)-I(X,Y)  \\
			&=& -\sum_y p(y)\log p(y) - \sum_{x,y}\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_y\left(\sum_x p(x,y)\right)\log p(y) - \sum_{x,y}p(x,y)\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_{x,y}p(x,y)\log p(y) - \sum_{x,y}\log\frac{p(x,y)}{p(x)p(y)} \\
			&=& -\sum_{x,y}p(x,y)\log\frac{p(x,y)}{p(x)} \\
			&=& -\sum_{x,y}p(x,y)\log p(y|x) = H(Y|X)
		\end{eqnarray*}
		According the formula (7):
		$$I(X,Y) = H(X)+H(Y)-H(X,Y)$$
	\end{frame}

	\begin{frame}
		\frametitle{Maximum Entropy Models}
		\textbf{The principle of maximum entropy states} that, subject to precisely stated prior data, the model which best represents the current state of knowledge is one with largest entropy.
		Given a sample collection, $$\mathcal{T}=\{(x_1,y_1),(x_2,y_2),\ldots,(x_N,y_N)\}$$
		Where $\mathcal{X}=\{x_1,\ldots,x_N\}$ is input set, $\mathcal{Y}=\{y_1,\ldots,y_N\}$ is output set. Our goal is to chose a best classifier which can output $y$ according to probability distribution $p(y|x)$.

	\begin{frame}
		\frametitle{Maximum Entropy Models(2)}

	\end{frame}
\end{document}
